---
title: "Regression Models course project: mtcars data set analysis"
author: "Enrico Gaffo"
date: "27/10/2015"
output: html_document
---

Context

You work for Motor Trend, a magazine about the automobile industry. Looking at 
a data set of a collection of cars, they are interested in exploring the 
relationship between a set of variables and miles per gallon (MPG) (outcome). 
They are particularly interested in the following two questions:

 - “Is an automatic or manual transmission better for MPG”
 - "Quantify the MPG difference between automatic and manual transmissions"

Take the mtcars data set and write up an analysis to answer their question
using regression models and exploratory data analyses.


```{r, echo=TRUE}
data(mtcars)
# mpg    Miles/(US) gallon
# am    Transmission (0 = automatic, 1 = manual)
summary(mtcars[, c("mpg", "am")])
boxplot(mpg ~ am, data = mtcars, ylab = "Miles/(US) gallon", xlab = "0 = automatic, 1 = manual")
stripchart(mpg ~ am, data = mtcars, vertical = T, method = "jitter",
           add = TRUE, pch = 16, col = 'blue')
```

The boxplot above shows that there is a clear increase in miles per gallon for manual transmission.


```{r, echo=TRUE}
fit <- lm(mpg ~ am, data = mtcars)
summary(fit)
```

The manual transmission increases average miles per gallon (mpg) (`r round(fit$coefficients[2], 2)` mpg more than the average mpg in automatic transmission vehicles). Hence, manual transmission has better performance, reducing fuel consumption.
The average mpg driven by automatic transmission vehicles is `r round(fit$coefficients[1], 2)`, 
while the average mpg manual transmission vehicles is `r round(fit$coefficients[1] + fit$coefficients[2], 2)` mpg, 

```{r, echo=TRUE}
par(mfrow = c(2, 2))
plot(fit)
```



```{r, echo=TRUE}
cor(mtcars)
fit.all <- lm(mpg ~ am + ., data = mtcars)
summary(fit.all)
```



Your report must be: 
Written as a PDF printout of a compiled (using knitr) R markdown document. 
Brief. Roughly the equivalent of 2 pages or less for the main text. Supporting
figures in an appendix can be included up to 5 total pages including the 2 for
the main report. The appendix can only include figures. Include a first
paragraph executive summary. Upload your PDF by clicking the Upload button
below the text box.

Did the student interpret the coefficients correctly?
Did the student do some exploratory data analyses?
Did the student fit multiple models and detail their strategy for model selection?
Did the student answer the questions of interest or detail why the question(s) is (are) not answerable?
Did the student do a residual plot and some diagnostics?
Did the student quantify the uncertainty in their conclusions and/or perform an inference correctly?
Was the report brief (about 2 pages long) for the main body of the report and no longer than 5 with supporting appendix of figures?
Did the report include an executive summary?
Was the report done in Rmd (knitr)?

